Linear vertical shear instability in astrophysical disks: a numerical study

### 2014-12-14 linear_iso.tex
minor update with notes

@@

>>>>

{\bf implicit limit on domain size. cannot be too large, otherwise omega reaches small values. should remain of order
omegak}

@@

{\bf get very similar result for if we replaced $\kappa^2(z)$ by $\Omega^2(z)$ instead. then the $(1+\hat{k}^2)$ factor should be 
inside integral with extra factor of $\Omega_k^2/\Omega^2$ multiplying the $\hat{k}^2$. but for subkeplerian disks $\Omega^2<\Omega_k^2$ so can replace
$\Omega^2$ by $\Omega^2_k$ without affecting the inequality on the lhs. on rhs need to replace $f$ by $\tilde{f}\equiv f\Omega_k^2/\Omega^2$. inequality is then not very 
useful if zmax is very large since $\Omega^2$ may reach small values or even zero at finite height , so $\mathrm{max}|\tilde{f}|$ is large or infinite. 
but still useful for zmax not too large such that $\Omega^2$ is similar to $\Omega^2$.}

{\bf zmax is limited by: $\Omega^2$ and $\kappa^2$ do not become small, since low frequency assumption will fail if domain reaches heights such that $\Omega\sim0$. also can't assume
$\Omega$ or $\kappa^2$ is roughly constant in coefficient of ode. (vertical derivatives always kept explicitly) 	
}
